Supplementary Appendix

### 2022-08-17 paper/appendix.qmd
uh

---
title: Supplementary Appendix
format:
    html: 
        standalone: true
        code-fold: true
        execute:
            echo: true
            eval: false
            warning: false
    gfm:
        wrap: none
        execute:
            echo: false
            eval: false
            warning: false
jupyter: julia-1.7
---

>>>>

---
title: Supplementary Appendix
format:
    html: 
        self-contained: true
        code-fold: true
        execute:
            echo: true
            eval: false
            warning: false
jupyter: julia-1.7
---
